When Risk Hits the Road: Does Danger Drive a Return?

### 2024-12-13 paper/paper.qmd
Add link of the questionnaire to appendix

The primary estimand of the analysis is the composite risk score, derived from the individual probabilities of motorbike theft and collision. This score is calculated using predictor variables such as neighborhood characteristics, road and lighting conditions, time of day, and other contextual factors, which were selected for their documented relevance to motorbike-related risks.

@@

```{r}
#| label: fig-risk-index-lighting-conditions
#| fig-cap: "Risk Index by Lighting Conditions"
#| fig-subcap: ["Low Light (Dark)", "Dawn Light", "Bright Daylight and Artificial Light", "Artificial Lighting Conditions"]
#| echo: false
#| warning: false
#| message: false
#| fig-width: 8.5
#| fig-height: 3.5
#| layout-ncol: 2
#| layout-nrow: 2

@@

Dark Conditions in @fig-risk-index-lighting-conditions-1 highlights a concentration of Risk Index values in the moderate-to-high range, indicating that low visibility during dark conditions significantly contributes to elevated collision risks. These findings underscore the importance of improved street lighting or reflective road markers in mitigating risks under dark conditions.

@@

## Survey structure and Content

The survey is structured into six main sections, each designed to gather detailed information about factors influencing motorbike risks.

**1. Demographics**

This section collects essential background information to contextualize the respondent's behaviors and risks:

- Age
- Gender
- Education level
- Income range
- Geographic location (urban, suburban, rural)
- Motorbike ownership status

**2. Motorbike Usage Patterns**

Questions in this section aim to understand how respondents use their motorbikes:

- Frequency of use (e.g., daily, weekly, monthly)
- Primary purpose (e.g., commuting, recreation, delivery work)
- Average trip duration
- Type of roads frequently used (e.g., highways, city streets, rural roads)
- Riding seasonality (e.g., year-round, summer-only)

**3. Riding Behavior**

This section looks into behaviors that may influence collision and theft risks:

- Average speed during rides
- Use of safety gear (e.g., helmets, gloves, reflective clothing)
- Adherence to traffic laws (e.g., stopping at signals, avoiding speeding)
- Riding under adverse conditions (e.g., rain, low light)
- Group riding versus solo riding

**4. Situational Risk Factors**

This section explores external factors that contribute to motorbike risks:

- Time of day most frequently ridden (morning, afternoon, night)
- Common weather conditions experienced (e.g., sunny, rainy, foggy)
- Road surface conditions during rides (e.g., dry, wet, icy)
- Presence of traffic control measures on roads used
- Experience with poorly lit or visibility-compromised areas

**5. Risk Awareness and Experience**

This section assesses respondents' awareness of risks and their personal experiences:

- Perception of collision and theft risks in their area
- Personal experience with motorbike theft (e.g., number of thefts, recovered cases)
- Personal experience with collisions (e.g., frequency, severity, injuries sustained)
- Awareness of high-risk areas for theft or collisions
- Perception of environmental risks (e.g., poor road design, lack of lighting)

**6. Preventive Measures and Interventions**

This section investigates actions taken by riders to mitigate risks and their opinions on potential interventions:

- Security measures used to prevent theft (e.g., locks, alarms, GPS trackers)
- Riding adjustments to avoid collisions (e.g., avoiding high-risk areas, reducing     speed)
- Willingness to participate in safety programs (e.g., high-level riding courses)
  Opinions on public safety measures (e.g., improved lighting, better road   
  infrastructure
- Suggestions for reducing theft and collisions in their area

### Question Types

To ensure the survey collects meaningful, diverse, and actionable data, a combination of question types will be used. Each type serves a specific purpose, enabling both quantitative analysis and qualitative understanding. Below are the key question types included in the survey:

@@

6. Drop-Down Questions

Drop-down questions are useful for limiting the display of options while allowing respondents to choose from a broad range of answers.

7. Conditional/Follow-Up Questions

Conditional questions are used to customize the survey based on previous responses, ensuring relevance and efficiency.

#### Question List

**Demographics**

1. What is your age group?

- Under 18

- 18-24

- 25-34

- 35-44

- 45-54

- 55+

2. What is your highest level of education?

- High school or less

- Some college or university

- Bachelor’s degree

- Master’s degree

- Doctorate or professional degree

**Motorbike Usage Patterns**

3. How frequently do you use your motorbike?

- Daily

- Weekly

- Monthly

- Rarely

- Other

4. How important are the following reasons for riding a motorbike to you?

- Commuting

- Recreation

- Delivery work

- Other

(Rank each reason: Not important at all, Slightly important, Moderately important, Very important, Extremely important)

**Riding Behavior**

5. How often do you wear a helmet while riding?

- Never

- Rarely

- Sometimes

- Often

- Always

6. What is your average speed while riding?

- Below 40 km/h

- 40-60 km/h

- 60-80 km/h

- Above 80 km/h

**Situational Risk Factors**

7. What time of day do you most often ride?

- Morning (6 AM–12 PM)

- Afternoon (12 PM–6 PM)

- Night (6 PM–12 AM)

- Early morning (12 AM–6 AM)

8. How often do you encounter poor road visibility during rides?

- Never

- Rarely

- Sometimes

- Often

**Risk Awareness and Experience**

9. Have you ever had your motorbike stolen?

- Yes

- No

(If "Yes," follow-up: How many times has your motorbike been stolen?)

- Once

- 2-3 times

- More than 3 times

10. How would you rate the risk of collisions in your area?

- Very low

- Low

- Moderate

- High

- Very high

11. How important are the following factors for motorbike safety?

- Helmet use

- Speed limits

- Visibility

(Rate each factor: Not important at all, Slightly important, Moderately important, Very important, Extremely important)

**Preventive Measures**

12. What security measures do you currently use to prevent motorbike theft?
(Select all that apply)

- Locks

- Alarms

- GPS trackers

- Other

13. How effective do you think these changes would be in reducing motorbike collisions in your area?

(Rate each factor: Not effective at all, Slightly effective, Moderately effective, Very effective, Extremely effective)

- Improved road lighting

-Better road maintenance (e.g., fixing potholes, clearing debris)

- Increased police patrols in high-risk areas

- Public education on motorbike safety

- Enforcing speed limits

14. What changes do you think would most effectively reduce motorbike collisions in your area?
(Open-ended)

>>>>

The **primary estimand** of the analysis is the composite risk score, derived from the individual probabilities of motorbike theft and collision. This score is calculated using predictor variables such as neighborhood characteristics, road and lighting conditions, time of day, and other contextual factors, which were selected for their documented relevance to motorbike-related risks.

@@

```{r}
#| label: fig-risk-index-lighting-conditions
#| fig-cap: "Risk Index by Lighting Conditions"
#| fig-subcap: ["Dark Light Conditions", "Daylight Conditions", "Dawn Light", "Artificial Lighting Conditions"]
#| echo: false
#| warning: false
#| message: false
#| fig-width: 8.5
#| fig-height: 3.5
#| layout-ncol: 2
#| layout-nrow: 2

@@

Dark Light Conditions in @fig-risk-index-lighting-conditions-1 highlights a concentration of Risk Index values in the moderate-to-high range, indicating that low visibility during dark conditions significantly contributes to elevated collision risks. These findings underscore the importance of improved street lighting or reflective road markers in mitigating risks under dark conditions.

@@

## Survey Structure and Content

Link to the survey: [Motorbike Safety and Risk Assessment Survey](https://forms.office.com/Pages/ResponsePage.aspx?id=DQSIkWdsW0yxEjajBLZtrQAAAAAAAAAAAANAAWz9FNNUN1pHR0haWjJUSU1LTVlDVkFFVVVMQjJUTy4u)

@@
